\textbf{ CMCS 818J Project Milestone Report } \\ \small{Christopher Imbriano \& Behzad Koosha}

### 2012-11-02 doc/milestone_draft1.tex
milestone_draft

%In the following, we will represent the steps that the streaming authenticated data structure follows to implement range search queries.
Taking into account that the bottomline of our scheme is the Merkle tree structure and using lattice based hash
function with homomorphic property, we are implementing the algorithm in Ruby language at this stage and 
defining classes for actually testing and configuring different steps in the algorithm. \\

Languages such as Python or Ruby support

\subsection{ Parts completed so far}

We started by to generate a secret and public key depending on the size of the stream and the 
security parameter. The next step was to generate the hash function according to each left and right leaf. 
The hash function is computed as $ h(x,y) = Lx + Ry $ where \textbf{L, R} are selected randomly from $Z_{q}^{k \times m}$ and
\textbf{x,y} are vectors of small norm.

@@

\subsection{ 2: Initialization}
%\label{initialize}

@@

\subsection{ 3: updateVerifier}
%\subsubsection{Inputs}
%\begin{enumerate}
%\item $x$ where $x \in \mathcal{U}$ is the current element of the stream
%\item $d_{h}$ current state of $auth(D_{h})$
%\item sk and pk - secret and public key \\
%\end{enumerate}
% 
% \subsubsection{Outputs}
% \begin{enumerate}
% \item $d_{h + 1}$ updated state of $auth(D_{h + 1})$
% \end{enumerate}
% 
% \begin{equation}
% d_{h+1} = d_{h} + \mathcal{D}_{r}(x, \textbf{1})
% \end{equation}
% 
% \subsubsection{Example}
% 
% \begin{itemize}
% \item $\mathcal{U} = \{ 0, 1, 2, 3, 4, 5, 6, 7\}$ similar to example in figure 7.1
% \item Suppose $x = 3$
% \end{itemize}
% 
% Calculating $d_{h + 1}$ reduces to calculating 	$ \mathcal{D}_{r}(x, \textbf{1})$ because $d_{h}$ is known.  \\
% 
% In our case, we'd like to calculate $\mathcal{D}_{r}(3, \textbf{1})$, i.e. the digest of the root node with respect 3. \\
% 
% By definition 10, 
% \begin{equation}
% \mathcal{D}_{r}(3, \textbf{1}) = \textbf{L} \cdot \textbf{b}(\mathcal{D}_{v_{11}}(3, \textbf{x}_{3})) 
% \end{equation}
% where $v_{11}$ is the left child of $r$, and $\mathcal{D}_{v_{11}}$ is the partial digest of $v_{11}$.
% 
% This procedure continues for each internal node eventually reaching the leaf node. The partial digest of a leaf node, in our case, that representing the element $x = 3$ is given by:
% 
% \begin{equation}
% \mathcal{D}_{3}(3, \textbf{1}) = \textbf{1}
% \end{equation}
% 
% Substituting the calculated partial digests for each node in the path from the root to the updated leaf node results in:
% 
% \begin{equation}
% \mathcal{D}_{r}(3, \textbf{1}) = \textbf{L} \cdot \textbf{b} ( \textbf{R} \cdot \textbf{b} ( \textbf{R} \cdot \textbf{b} ( \textbf{1} ) )  )
% \end{equation}
% 
% Thus, the new digest for the entire tree is given by:
% \begin{equation}
% d_{h+1} = d_{h} + \textbf{L} \cdot \textbf{b} ( \textbf{R} \cdot \textbf{b} ( \textbf{R} \cdot \textbf{b} ( \textbf{1} ) )  )
% \end{equation}
% 
% %\subsection{Questions}
% %\begin{enumerate}
% %\item What are the roles of the secret and public key as inputs?  In the previous email, you said the prover generates the secret key and does not output it. Therefore, the verifier can't have any value here for $sk$ besides null.
% %\end{enumerate}
% 
% \subsection{ 4: updateProver}
% \subsubsection{Input}
% \begin{itemize}
% \item $x$: $x \in \mathcal{U}$ is the current element of the stream
% \item $pk$:  public key
% \item $D_{h}$: The table, \textbf{T} which represents leaves of the Merkle tree described by the scheme
% \item $auth(D_{h})$: The auxiliary information allowing authentication of the elements in $D_{h}$ including all labels $\lambda(v_{i})$ for internals nodes and $d_{h}$, the root digest of the whole tree.
% \end{itemize}
% \subsubsection{Output}
% 
% \begin{itemize}
% \item $D_{h + 1}$: Updated table \textbf{T}
% \item $auth(D_{h + 1})$: Updated labels and root digest
% \end{itemize}
% 
% \subsubsection{Example}
% 
% Using the same scenario as the verifier example where $x = 3$, the updated labels is given by:
% 
% \begin{equation}
% \lambda(v_{i}) = \lambda(v_{i}) + \textbf{b}( \mathcal{D}_{v_{i}}(3, \textbf{1}) ) \textrm{ for } i = \ell, \ell -1, \ldots, 1  
% \end{equation}
% 
% Calculating each $\lambda(v_{i})$ is straight forward.  In the last example, we understood how to calculate a partial digest, and the $\textbf{b}()$ function is well-defined.

>>>>

%In the following, we will represent the steps that the streaming authenticated data structure follows to implement range search queries.
Taking into account that the bottomline of our scheme is the Merkle tree structure and using lattice based hash
function with homomorphic property, we are implementing the algorithm in Python or Ruby language at this stage and 
actually testing and configuring different steps in the algorithm i.e. \texttt{genkey, initialize, updateVerifier, updateProver, query, verify}.   \\

Languages such as Python or Ruby have support for their community of users that grows up and that
is one of its most important strengths. Ruby has a vibrant and growing community that is friendly towards
people of all skill levels. Such groups allow users to network with other Ruby
programmers.  \\

As for Python, NumPy is an extension module which provides efficient operations on arrays of data allowing
Python to operate as a high level language for manipulating numerical data.
In addition, SciPy is a set of open source scientific and numerical tools for Python. It can 
support special functions, integration, differential equation solvers, etc. \\

We are also thinking to use some software system such as EventMachine that is designed for writing
scalable applications in Ruby. EventMachine has been used for making various libraries and frameworks
in which concurrency is considered. Examples of such application could be
web servers and proxies, email and IM, authentication and authorization processors and 
network applications. \\

In our work, we have generated a secret and public key depending on the size of the stream and the 
security parameter. The next step was to generate the hash function according to each left and right leaf. 
The hash function is computed as $ h(x,y) = Lx + Ry $ where \textbf{L, R} are selected randomly from $Z_{q}^{k \times m}$ and
\textbf{x,y} are vectors of small norm. \\

@@

%\subsection{ 2: Initialization}
%\label{initialize}

@@

%\subsection{ 3: updateVerifier}
%\subsubsection{Inputs}
%\begin{enumerate}
%\item $x$ where $x \in \mathcal{U}$ is the current element of the stream
%\item $d_{h}$ current state of $auth(D_{h})$
%\item sk and pk - secret and public key \\
%\end{enumerate}
% 
% \subsubsection{Outputs}
% \begin{enumerate}
% \item $d_{h + 1}$ updated state of $auth(D_{h + 1})$
% \end{enumerate}
% 
% \begin{equation}
% d_{h+1} = d_{h} + \mathcal{D}_{r}(x, \textbf{1})
% \end{equation}
% 
% \subsubsection{Example}
% 
% \begin{itemize}
% \item $\mathcal{U} = \{ 0, 1, 2, 3, 4, 5, 6, 7\}$ similar to example in figure 7.1
% \item Suppose $x = 3$
% \end{itemize}
% 
% Calculating $d_{h + 1}$ reduces to calculating 	$ \mathcal{D}_{r}(x, \textbf{1})$ because $d_{h}$ is known.  \\
% 
% In our case, we'd like to calculate $\mathcal{D}_{r}(3, \textbf{1})$, i.e. the digest of the root node with respect 3. \\
% 
% By definition 10, 
% \begin{equation}
% \mathcal{D}_{r}(3, \textbf{1}) = \textbf{L} \cdot \textbf{b}(\mathcal{D}_{v_{11}}(3, \textbf{x}_{3})) 
% \end{equation}
% where $v_{11}$ is the left child of $r$, and $\mathcal{D}_{v_{11}}$ is the partial digest of $v_{11}$.
% 
% This procedure continues for each internal node eventually reaching the leaf node. The partial digest of a leaf node, in our case, that representing the element $x = 3$ is given by:
% 
% \begin{equation}
% \mathcal{D}_{3}(3, \textbf{1}) = \textbf{1}
% \end{equation}
% 
% Substituting the calculated partial digests for each node in the path from the root to the updated leaf node results in:
% 
% \begin{equation}
% \mathcal{D}_{r}(3, \textbf{1}) = \textbf{L} \cdot \textbf{b} ( \textbf{R} \cdot \textbf{b} ( \textbf{R} \cdot \textbf{b} ( \textbf{1} ) )  )
% \end{equation}
% 
% Thus, the new digest for the entire tree is given by:
% \begin{equation}
% d_{h+1} = d_{h} + \textbf{L} \cdot \textbf{b} ( \textbf{R} \cdot \textbf{b} ( \textbf{R} \cdot \textbf{b} ( \textbf{1} ) )  )
% \end{equation}
% 
% %\subsection{Questions}
% %\begin{enumerate}
% %\item What are the roles of the secret and public key as inputs?  In the previous email, you said the prover generates the secret key and does not output it. Therefore, the verifier can't have any value here for $sk$ besides null.
% %\end{enumerate}
% 
% \subsection{ 4: updateProver}
% \subsubsection{Input}
% \begin{itemize}
% \item $x$: $x \in \mathcal{U}$ is the current element of the stream
% \item $pk$:  public key
% \item $D_{h}$: The table, \textbf{T} which represents leaves of the Merkle tree described by the scheme
% \item $auth(D_{h})$: The auxiliary information allowing authentication of the elements in $D_{h}$ including all labels $\lambda(v_{i})$ for internals nodes and $d_{h}$, the root digest of the whole tree.
% \end{itemize}
% \subsubsection{Output}
% 
% \begin{itemize}
% \item $D_{h + 1}$: Updated table \textbf{T}
% \item $auth(D_{h + 1})$: Updated labels and root digest
% \end{itemize}
% 
% \subsubsection{Example}
% 
% Using the same scenario as the verifier example where $x = 3$, the updated labels is given by:
% 
% \begin{equation}
% \lambda(v_{i}) = \lambda(v_{i}) + \textbf{b}( \mathcal{D}_{v_{i}}(3, \textbf{1}) ) \textrm{ for } i = \ell, \ell -1, \ldots, 1  
% \end{equation}
% 
% Calculating each $\lambda(v_{i})$ is straight forward.  In the last example, we understood how to calculate a partial digest, and the $\textbf{b}()$ function is well-defined.
